HEP Software Foundation Community White Paper Working Group -- Detector Simulation

### 2018-02-28 CWP/papers/HSF-CWP-2017-07_detsim/latex/DetectorSimulation.tex
2 more names on author list
corrected reference 4 to NOvA experiment

\author[c]{J Apostolakis}
\author[p]{M Asai}
\author[e]{S Banerjee}
\author[l]{R Bianchi}
\author[e]{P Canal}
\author[k]{R Cenci}
\author[b]{J Chapman}
\author[c]{G Corti}
\author[c]{G Cosmo}
\author[o]{S Easo}
\author[h]{L de Oliveira}
\author[p]{A Dotti}
\author[e,1]{V Elvira}
\author[e]{L Fields}
\author[e]{K Genser}
\author[c]{A Gheata}
\author[c]{M Gheata}
\author[c,1]{J Harvey}
\author[c]{F Hariri}
\author[e]{R Hatcher}
\author[e]{K Herner}
\author[j]{M Hildreth}
\author[c]{V Ivantchenko}
\author[e]{T Junk}
\author[e]{S-Y Jun}
\author[e]{M Kirby}
\author[m]{D Konstantinov}
\author[e]{R Kutschke}
\author[e]{P Lebrun}
\author[e]{G Lima}
\author[e]{A Lyon}
\author[h]{Z Marshall}
\author[c]{P Mato}
\author[a]{M Mooney}
\author[p]{R Mount}
\author[i]{J Mousseau}
\author[h]{B Nachman}
\author[e]{A Norman}
\author[c]{M Novak}
\author[e]{I Osborne}
\author[q]{M Paganini}
\author[e]{K Pedro}
\author[c]{W Pokorski}
\author[a]{X Qian}
\author[e]{J Raaf}
\author[k]{M Rama}
\author[c]{A Ribon}
\author[c]{S Roiser}
\author[n]{D Ruterbories}
\author[e]{S Sekmen}
\author[g]{B Siddi}
\author[e]{E Snider}
\author[f]{S Vallecorsa}
\author[d]{M Verderi}
\author[e]{H Wenzel}
\author[c]{S Wenzel}
\author[a]{B Viren}
\author[e]{T Yang}
\author[e]{J Yarba}
\author[e]{L Welty-Rieger}
\author[p]{D.H.Wright}

@@

There are specific challenges associated with the Intensity Frontier
experimental programme. Properly simulating a neutrino experiment like
NOvA ~\cite{1742-6596-396-2-022014}, MicroBooNE~\cite{MicroBooNE}, 
MINERvA~\cite{Aliaga:2013uqz}, or DUNE ~\cite{Acciarri:2015uup}
involves a three-part software stack, the first and last of which are
relevant to this paper; the second, event generators such as GENIE, 
is discussed elsewhere. The first element of the stack concerns
the beamline and the neutrino flux prediction. Estimating the neutrino
flux is a notorious problem because as weakly interacting particles,
neutrinos offer no independent mechanisms for measuring the flux. A
central problem is in the difficulty of accurately simulating the
hadronic physics of meson production, especially in a thick target.
Additionally, the simulated neutrino flux depends very strongly on
minute details of the beamline, meaning that neutrino beam kinematic
distributions must be described in great detail. Geant4 is the most
commonly used software toolkit for this work, although FLUKA ~\cite{Ferrari:2005zk} 
and MARS ~\cite{MARS} are also used. The final element of the stack is the
detector simulation. Again there are numerous challenges in terms of
efficiently simulating large numbers of events inside complex detector
geometries and in handling subtle physics effects in the traversal of
radiation across matter. Neutrino experiments in particular rely heavily
on detector simulations to reconstruct neutrino energy, which requires
accurate modeling of energy deposition by a variety of particles across
a range of energies. Geant4 is the universal solution at this stage.

>>>>

\author[c]{J Apostolakis}
\author[p]{M Asai}
\author[e]{S Banerjee}
\author[l]{R Bianchi}
\author[e]{P Canal}
\author[k]{R Cenci}
\author[b]{J Chapman}
\author[c]{G Corti}
\author[c]{G Cosmo}
\author[o]{S Easo}
\author[h]{L de Oliveira}
\author[p]{A Dotti}
\author[e,1]{V Elvira}
\author[h]{S Farrell}
\author[e]{L Fields}
\author[e]{K Genser}
\author[c]{A Gheata}
\author[c]{M Gheata}
\author[c,1]{J Harvey}
\author[c]{F Hariri}
\author[e]{R Hatcher}
\author[e]{K Herner}
\author[j]{M Hildreth}
\author[c]{V Ivantchenko}
\author[e]{T Junk}
\author[e]{S-Y Jun}
\author[e]{M Kirby}
\author[m]{D Konstantinov}
\author[e]{R Kutschke}
\author[e]{P Lebrun}
\author[e]{G Lima}
\author[e]{A Lyon}
\author[h]{Z Marshall}
\author[c]{P Mato}
\author[a]{M Mooney}
\author[p]{R Mount}
\author[i]{J Mousseau}
\author[h]{B Nachman}
\author[e]{A Norman}
\author[c]{M Novak}
\author[e]{I Osborne}
\author[q]{M Paganini}
\author[e]{K Pedro}
\author[c]{W Pokorski}
\author[a]{X Qian}
\author[e]{J Raaf}
\author[k]{M Rama}
\author[c]{A Ribon}
\author[c]{S Roiser}
\author[n]{D Ruterbories}
\author[e]{S Sekmen}
\author[g]{B Siddi}
\author[e]{E Snider}
\author[f]{S Vallecorsa}
\author[d]{M Verderi}
\author[e]{H Wenzel}
\author[c]{S Wenzel}
\author[a]{B Viren}
\author[e]{T Yang}
\author[e]{J Yarba}
\author[e]{L Welty-Rieger}
\author[p]{D H Wright}
\author[a]{C Zhang}

@@

There are specific challenges associated with the Intensity Frontier
experimental programme. Properly simulating a neutrino experiment like
NOvA ~\cite{Adamson:2016tbq}, MicroBooNE~\cite{MicroBooNE}, 
MINERvA~\cite{Aliaga:2013uqz}, or DUNE ~\cite{Acciarri:2015uup}
involves a three-part software stack, the first and last of which are
relevant to this paper; the second, event generators such as GENIE, 
is discussed elsewhere. The first element of the stack concerns
the beamline and the neutrino flux prediction. Estimating the neutrino
flux is a notorious problem because as weakly interacting particles,
neutrinos offer no independent mechanisms for measuring the flux. A
central problem is in the difficulty of accurately simulating the
hadronic physics of meson production, especially in a thick target.
Additionally, the simulated neutrino flux depends very strongly on
minute details of the beamline, meaning that neutrino beam kinematic
distributions must be described in great detail. Geant4 is the most
commonly used software toolkit for this work, although FLUKA ~\cite{Ferrari:2005zk} 
and MARS ~\cite{MARS} are also used. The final element of the stack is the
detector simulation. Again there are numerous challenges in terms of
efficiently simulating large numbers of events inside complex detector
geometries and in handling subtle physics effects in the traversal of
radiation across matter. Neutrino experiments in particular rely heavily
on detector simulations to reconstruct neutrino energy, which requires
accurate modeling of energy deposition by a variety of particles across
a range of energies. Geant4 is the universal solution at this stage.
